Lock-free Skiplist-based Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-02-20 paper/paper.tex
A sample abstract text

\begin{abstract}
blablablu blublubla
\end{abstract}

>>>>

\begin{abstract}
On the 24th of February, 1815, the watch-tower of Notre-Dame de la Garde
signalled the arrival of the three-master Pharaon, from Smyrna, Trieste, 
and Naples.

The usual crowd of curious spectators immediately filled the quay of Fort 
Saint-Jean, for at Marseilles the arrival of a ship is always a great event, 
especially when that ship, as was the case with the Pharaon, has been built, 
rigged, and laden in the dockyard of old Phocaea and belongs to a shipowner 
of their own town.

Meanwhile the vessel drew on, and was approaching the harbour under topsails, 
jib, and foresail, but so slowly and with such an air of melancholy that the 
spectators, always ready to sense misfortune, began to ask one another what 
ill-luck had overtaken those on board. However, those experienced in navigation 
soon saw that if there had been any ill-luck, the ship had not been the 
sufferer, for she advanced in perfect condition and under skilful handling; 
the anchor was ready to be dropped, the bowsprit shrouds loose. 
Beside the pilot, who was steering the Pharaon through the narrow entrance to 
the port, there stood a young man, quick of gesture and keen of eye, who 
watched every movement of the ship while repeating each of the pilot's orders.
\end{abstract}
